### 2019-02-27 soc.tex
load titlesec package before hyperref package
This should fix the issue with references pointing to wrong chapters.
update consultant
translate website load time table to czech and lexicographically sort it

@@

% TEXT FORMATTING %
%-================-%
\usepackage{titlesec}

% titles have sizes 18pt, 16pt and 14pt, respectively
% the space between the number and the text of the title is 1em
\titleformat{\section}{\bfseries\scshape\fontsize{18pt}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16pt}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14pt}{16.8}\selectfont}{\thesubsubsection}{1em}{}

\setlength\parindent{0pt}                       % 0pt paragraph indentation
\setlength\parskip{12pt}                        % 12pt paragraph spacing

\renewcommand{\baselinestretch}{1.15}           % baseline stretch

@@

  \textbf{Autoři:} Tomáš Sláma\\
  \textbf{Škola:} Gymnázium, Turnov, Jana Palacha 804, příspěvková \\ organizace, 511 21 Turnov \\
  \textbf{Kraj:} Liberecký kraj \\
  \textbf{Konzultant:} Mgr. Tomáš Novotný

@@

    Buenos Aires, Argentina & \href{https://www.webpagetest.org/result/190213_PC_5d05753a2ce2126089db6b8726171c13}{\texttt{190213\_PC\_5d05753a2ce2126089db6b8726171c13}} \\
    Toronto, Canada         & \href{https://www.webpagetest.org/result/190213_44_a861d3caa2bdbb547775b76e0ca7e357}{\texttt{190213\_44\_a861d3caa2bdbb547775b76e0ca7e357}} \\
    La Rioja, Spain         & \href{https://www.webpagetest.org/result/190213_ZA_96b8ca66a5af8d0bbee48a48d1ebf901}{\texttt{190213\_ZA\_96b8ca66a5af8d0bbee48a48d1ebf901}} \\
    Prague, Czech Republic  & \href{https://www.webpagetest.org/result/190213_SD_119a43e321c4360178004f09bb4d27a0}{\texttt{190213\_SD\_119a43e321c4360178004f09bb4d27a0}} \\
    London, UK              & \href{https://www.webpagetest.org/result/190213_SS_1226a99822746d3cf16fb81bd19c9ac8}{\texttt{190213\_SS\_1226a99822746d3cf16fb81bd19c9ac8}} \\
    Strasburg, France       & \href{https://www.webpagetest.org/result/190213_35_5db33eb4e90d8b096d8853fa453d54d3}{\texttt{190213\_35\_5db33eb4e90d8b096d8853fa453d54d3}} \\
    Brussels, BE            & \href{https://www.webpagetest.org/result/190213_PK_8973798f51f040a199501b3332071bc2}{\texttt{190213\_PK\_8973798f51f040a199501b3332071bc2}} \\
    Berlin, Germany         & \href{https://www.webpagetest.org/result/190213_S3_321db7231844fc993d91fba974e569bb}{\texttt{190213\_S3\_321db7231844fc993d91fba974e569bb}} \\
    Milan, Italy            & \href{https://www.webpagetest.org/result/190213_QE_7d2d0c62fe56d0a992f83872fea9589a}{\texttt{190213\_QE\_7d2d0c62fe56d0a992f83872fea9589a}} \\
    Warsaw, Poland          & \href{https://www.webpagetest.org/result/190213_AV_e12420619d2b67b02b36fd8f85012634}{\texttt{190213\_AV\_e12420619d2b67b02b36fd8f85012634}} \\
    Stockholm, Sweden       & \href{https://www.webpagetest.org/result/190213_PC_8bf596590b3cb93164fb6b20e2ae9b7a}{\texttt{190213\_PC\_8bf596590b3cb93164fb6b20e2ae9b7a}} \\
    Istanbul, Turkey        & \href{https://www.webpagetest.org/result/190213_FZ_3eb94a70dfdd8c92bcfcfaf74a412501}{\texttt{190213\_FZ\_3eb94a70dfdd8c92bcfcfaf74a412501}} \\
    Israel                  & \href{https://www.webpagetest.org/result/190213_XT_735a3f35ee6a8056ad47aac3d5a95917}{\texttt{190213\_XT\_735a3f35ee6a8056ad47aac3d5a95917}} \\
    Dubai, UAE              & \href{https://www.webpagetest.org/result/190213_66_d158a4ae09a1ef5d63b68693b5230066}{\texttt{190213\_66\_d158a4ae09a1ef5d63b68693b5230066}} \\
    Seoul, Korea            & \href{https://www.webpagetest.org/result/190213_TX_d56f64b9948b96bdfdd1323fd16b0867}{\texttt{190213\_TX\_d56f64b9948b96bdfdd1323fd16b0867}} \\
    Mumbai, India           & \href{https://www.webpagetest.org/result/190213_ED_2a0542955442372c423c9306a7492c02}{\texttt{190213\_ED\_2a0542955442372c423c9306a7492c02}} \\
    Amsterdam, NL           & \href{https://www.webpagetest.org/result/190213_37_88f29978d6231e700fe963b8d943a79b}{\texttt{190213\_37\_88f29978d6231e700fe963b8d943a79b}} \\
    Sydney, Australia       & \href{https://www.webpagetest.org/result/190213_8N_c4802d60f2820dd2b7f8e3e5d6a384c1}{\texttt{190213\_8N\_c4802d60f2820dd2b7f8e3e5d6a384c1}} \\
    Clifton, NJ             & \href{https://www.webpagetest.org/result/190213_3S_570bc4b76dd084486a1ae6ba1829f2cc}{\texttt{190213\_3S\_570bc4b76dd084486a1ae6ba1829f2cc}} \\
    Jakarta, Indonesia      & \href{https://www.webpagetest.org/result/190213_12_db0913a1b2708f54db46d5d40b7f61e5}{\texttt{190213\_12\_db0913a1b2708f54db46d5d40b7f61e5}} \\
    Tokyo, Japan            & \href{https://www.webpagetest.org/result/190213_8Q_083b45677c2c51f4fe7bd25b554dff38}{\texttt{190213\_8Q\_083b45677c2c51f4fe7bd25b554dff38}} \\
    Sao Paulo, Brazil       & \href{https://www.webpagetest.org/result/190213_AD_d2d6ea6b39f36853cf476a5f1d1f3092}{\texttt{190213\_AD\_d2d6ea6b39f36853cf476a5f1d1f3092}} \\
    Vietnam                 & \href{https://www.webpagetest.org/result/190213_RQ_18f2a02931599884f8922a3ce09f56bc}{\texttt{190213\_RQ\_18f2a02931599884f8922a3ce09f56bc}} \\
    Hong Kong, China        & \href{https://www.webpagetest.org/result/190213_NK_dfd8ddf4b9766b3386799de124a67ad8}{\texttt{190213\_NK\_dfd8ddf4b9766b3386799de124a67ad8}} \\

>>>>

\usepackage{titlesec}

% TITLE FORMATTING %
%-================-%
% titles have sizes 18pt, 16pt and 14pt, respectively
% the space between the number and the text of the title is 1em
\titleformat{\section}{\bfseries\scshape\fontsize{18pt}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16pt}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14pt}{16.8}\selectfont}{\thesubsubsection}{1em}{}

@@

% PARAGRAPH FORMATTING %
%-====================-%
\setlength\parindent{0pt}                       % 0pt paragraph indentation
\setlength\parskip{12pt}                        % 12pt paragraph spacing

\renewcommand{\baselinestretch}{1.15}           % baseline stretch is 1.15

@@

  \textbf{Autoři:} Tomáš Sláma\\
  \textbf{Škola:} Gymnázium, Turnov, Jana Palacha 804, příspěvková \\ organizace, 511 21 Turnov \\
  \textbf{Kraj:} Liberecký kraj \\
  \textbf{Konzultant:} Ing. Daniel Kajzr

@@

    Argentina (Buenos Aires)        & \href{https://www.webpagetest.org/result/190213_PC_5d05753a2ce2126089db6b8726171c13}{\texttt{190213\_PC\_5d05753a2ce2126089db6b8726171c13}} \\
    Austrálie (Sydney)              & \href{https://www.webpagetest.org/result/190213_8N_c4802d60f2820dd2b7f8e3e5d6a384c1}{\texttt{190213\_8N\_c4802d60f2820dd2b7f8e3e5d6a384c1}} \\
    Belgie (Brusel)                 & \href{https://www.webpagetest.org/result/190213_PK_8973798f51f040a199501b3332071bc2}{\texttt{190213\_PK\_8973798f51f040a199501b3332071bc2}} \\
    Brazílie (Sao Paulo)            & \href{https://www.webpagetest.org/result/190213_AD_d2d6ea6b39f36853cf476a5f1d1f3092}{\texttt{190213\_AD\_d2d6ea6b39f36853cf476a5f1d1f3092}} \\
    Česká republika (Praha)         & \href{https://www.webpagetest.org/result/190213_SD_119a43e321c4360178004f09bb4d27a0}{\texttt{190213\_SD\_119a43e321c4360178004f09bb4d27a0}} \\
    Čína (Hong Kong)                & \href{https://www.webpagetest.org/result/190213_NK_dfd8ddf4b9766b3386799de124a67ad8}{\texttt{190213\_NK\_dfd8ddf4b9766b3386799de124a67ad8}} \\
    Francie (Strasburg)             & \href{https://www.webpagetest.org/result/190213_35_5db33eb4e90d8b096d8853fa453d54d3}{\texttt{190213\_35\_5db33eb4e90d8b096d8853fa453d54d3}} \\
    Indie (Mumbai)                  & \href{https://www.webpagetest.org/result/190213_ED_2a0542955442372c423c9306a7492c02}{\texttt{190213\_ED\_2a0542955442372c423c9306a7492c02}} \\
    Indonésie (Jakarta)             & \href{https://www.webpagetest.org/result/190213_12_db0913a1b2708f54db46d5d40b7f61e5}{\texttt{190213\_12\_db0913a1b2708f54db46d5d40b7f61e5}} \\
    Itálie (Milán)                  & \href{https://www.webpagetest.org/result/190213_QE_7d2d0c62fe56d0a992f83872fea9589a}{\texttt{190213\_QE\_7d2d0c62fe56d0a992f83872fea9589a}} \\
    Izrael (neurčeno)               & \href{https://www.webpagetest.org/result/190213_XT_735a3f35ee6a8056ad47aac3d5a95917}{\texttt{190213\_XT\_735a3f35ee6a8056ad47aac3d5a95917}} \\
    Japonsko (Tokio)                & \href{https://www.webpagetest.org/result/190213_8Q_083b45677c2c51f4fe7bd25b554dff38}{\texttt{190213\_8Q\_083b45677c2c51f4fe7bd25b554dff38}} \\
    Jižní Korea (Soul)              & \href{https://www.webpagetest.org/result/190213_TX_d56f64b9948b96bdfdd1323fd16b0867}{\texttt{190213\_TX\_d56f64b9948b96bdfdd1323fd16b0867}} \\
    Kanada (Toronto)                & \href{https://www.webpagetest.org/result/190213_44_a861d3caa2bdbb547775b76e0ca7e357}{\texttt{190213\_44\_a861d3caa2bdbb547775b76e0ca7e357}} \\
    Nizozemí (Amsterdam)            & \href{https://www.webpagetest.org/result/190213_37_88f29978d6231e700fe963b8d943a79b}{\texttt{190213\_37\_88f29978d6231e700fe963b8d943a79b}} \\
    Německo (Berlín)                & \href{https://www.webpagetest.org/result/190213_S3_321db7231844fc993d91fba974e569bb}{\texttt{190213\_S3\_321db7231844fc993d91fba974e569bb}} \\
    Polsko (Varšava)                & \href{https://www.webpagetest.org/result/190213_AV_e12420619d2b67b02b36fd8f85012634}{\texttt{190213\_AV\_e12420619d2b67b02b36fd8f85012634}} \\
    Spojené arabské emiráty (Dubaj) & \href{https://www.webpagetest.org/result/190213_66_d158a4ae09a1ef5d63b68693b5230066}{\texttt{190213\_66\_d158a4ae09a1ef5d63b68693b5230066}} \\
    Spojené království (Londýn)     & \href{https://www.webpagetest.org/result/190213_SS_1226a99822746d3cf16fb81bd19c9ac8}{\texttt{190213\_SS\_1226a99822746d3cf16fb81bd19c9ac8}} \\
    Španělsko (La Rioja)            & \href{https://www.webpagetest.org/result/190213_ZA_96b8ca66a5af8d0bbee48a48d1ebf901}{\texttt{190213\_ZA\_96b8ca66a5af8d0bbee48a48d1ebf901}} \\
    Švédsko (Stockholm)             & \href{https://www.webpagetest.org/result/190213_PC_8bf596590b3cb93164fb6b20e2ae9b7a}{\texttt{190213\_PC\_8bf596590b3cb93164fb6b20e2ae9b7a}} \\
    Turecko (Istanbul)              & \href{https://www.webpagetest.org/result/190213_FZ_3eb94a70dfdd8c92bcfcfaf74a412501}{\texttt{190213\_FZ\_3eb94a70dfdd8c92bcfcfaf74a412501}} \\
    USA (Clifton)                   & \href{https://www.webpagetest.org/result/190213_3S_570bc4b76dd084486a1ae6ba1829f2cc}{\texttt{190213\_3S\_570bc4b76dd084486a1ae6ba1829f2cc}} \\
    Vietnam (neurčeno)              & \href{https://www.webpagetest.org/result/190213_RQ_18f2a02931599884f8922a3ce09f56bc}{\texttt{190213\_RQ\_18f2a02931599884f8922a3ce09f56bc}} \\
